\documentclass{article}%
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{hyperref}%
\setcounter{MaxMatrixCols}{30}
%TCIDATA{OutputFilter=latex2.dll}
%TCIDATA{Version=5.00.0.2552}
%TCIDATA{CSTFile=40 LaTeX article.cst}
%TCIDATA{Created=Thursday, August 21, 2008 14:03:59}
%TCIDATA{LastRevised=Wednesday, October 01, 2014 12:46:33}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{<META NAME="DocumentShell" CONTENT="Standard LaTeX\Blank - Standard LaTeX Article">}
%TCIDATA{Language=American English}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\begin{document}

\title{Homework 3}


\author{Christopher Chapline}
\maketitle

\section{Exercise 3.1}

\subsection{Part a}
$\Sigma*gc\Sigma*$

\subsection{Part b}
$(\Sigma*(g + \epsilon)(\Sigma - c))*$

\subsection{Part c}
$(g + c + (t((aa) + (ata) + (tt))*)*)$

\subsection{Part d}
$(c + a + t + (g(c(g + c + t + \epsilon) + \epsilon) + \epsilon))*$

\section{Exercise 3.2}

\subsection{Part a}
$([A-Z] + [a-z])([A-Z] + [a-z] + [0-9])*$

\subsection{Part b}
$[0-9]*.[0-9][0-9]*$

\subsection{Part c}
$\Sigma \Sigma*.\Sigma \Sigma*.((com) + (org) + (edu))$

\subsection{Part d}
$({\ } + \setminus t + \setminus n)*$ where {\_}

\section{Exercise 3.3}
First we need to find instances in which there are multiple newline characters. These are paragraph separations and should be
marked. We mark them by assigning them a special character sequence (\&\& in this case): \\

replace("\setminus n \setminus n", "\&\&") \\

\noindent Now we replace singular newlines with a whitespace. This will condense simple line breaks into sentences: \\

replace("\setminus n", "{\ }") \\

\noindent Lastly, we replace the previously substituted paragraph breaks with actual newline characters \\

replace("\&\&", "\setminus n \setminus n") \\

\section{Exercise 3.4}

\subsection{Part a}
$[A-Z][a-z]*'{\ }'([A-Z](. + [a-z]*)'{\ }' + \epsilon)[A-Z][a-z]*('{\ }'Jr + \epsilon)$

\subsection{Part b}
$[A-Z][a-z]*,[A-Z][a-z]*(('{\ }'[A-Z](. + [a-z]*)) + \epsilon)$

\subsection{Part c}
$([0-9]([0-9] + \epsilon)'{\ }'[A-Z][a-z]*'{\ }'[0-9][0-9][0-9][0-9]) +$ \\
$([A-Z][a-z]*'{\ }'[0-9]([0-9] + \epsilon)'{\ }'[0-9][0-9][0-9][0-9]) +$ \\
$([[0-9][0-9][0-9][0-9]'{\ }'[A-Z][a-z]*'{\ }'[0-9]([0-9] + \epsilon))$


\section{Exercise 3.5}

\subsection{Part a}
replace("{\ }or{\ }", "{\ }\&\&{\ }") \\
replace("or{\ }", "our{\ }") \\
replace("\&\&", "or") \\

\noindent replace("{\ }er{\ }", "{\ }\&\&{\ }") \\
replace("er{\ }", "re{\ }") \\
replace("\&\&", "er") \\

\subsection{Part b}
For the "or" $\rightarrow$ "our" mapping, this conflicts with words like "floor" and "moor". For the "er" $\rightarrow$ "re"
mapping, flayer and computer conflict. These could all be handled by replacing them with custom strings prior to the primary
replace calls. These custom strings would be changed back afterwards. This is similar to how the words "or" and "our" were handled.

\end{document}
